Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-02-10 paper/ms.tex
sho typo
updating some examples
cleaning up a bit [ci skip]

Another special case of the \celerite\ model of great physical interest is a
stochastically-driven simple harmonic oscillator.
The differential equation for this system is
\begin{equation}
    \left[\frac{\dd^2}{\dd t^2} + \frac{\omega_0}{Q}\,\frac{\dd}{\dd t}
    + \omega_0^2\right]\, y(t) = \epsilon(t)
\end{equation}
where $\omega_0$ is the frequency of the undamped oscillator, $Q$ is the
quality factor of the oscillator, and $\epsilon(t)$ is a stochastic driving
force.
In the limit of an infinite time series and white random forcing, the PSD of
this equation is given by \citep{Anderson:1990}
\begin{equation}\eqlabel{sho-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0\,\omega_0^4}
    {(\omega^2-\omega_0^2)^2 + \omega_0^2\omega^2/Q^2}
\end{equation}
where $S_0$ is proportional to the power at $\omega = \omega_0$, $S(\omega_0)
= \sqrt{2/\pi}\,S_0$.
The power spectrum in \eq{sho-psd} matches \eq{celerite-psd} if
\begin{eqnarray}\eqlabel{sho-complex}
a_j &=& S_0\,\omega_0\,Q \\
b_j &=& \frac{S_0\,\omega_0\,Q}{\sqrt{4\,Q^2-1}} \\
c_j &=& \frac{\omega_0}{2\,Q}\\
d_j &=& \frac{\omega_0}{2\,Q} \sqrt{4\,Q^2-1} \quad,
\end{eqnarray}
for $Q \ge \frac{1}{2}$.
For $0 < Q \le \frac{1}{2}$, \eq{sho-psd} can be captured by a pair of \celerite\
terms with parameters
\begin{eqnarray}\eqlabel{sho-real}
a_{j\pm} &=& \frac{1}{2}\,S_0\,\omega_0\,Q\,\left[ 1 \pm
        \frac{1}{\sqrt{1-4\,Q^2}}\right] \\
b_{j\pm} &=& 0 \nonumber\\
    c_{j\pm} &=& \frac{\omega_0}{2\,Q}\,\left[1 \mp \sqrt{1-4\,Q^2}\right]
    \nonumber\\
d_{j\pm} &=& 0 \quad. \nonumber
\end{eqnarray}

@@

\begin{enumerate}
\item Asteroseismic target
\item Stellar rotation variability
\item Kepler with simulated transit
\item AGN
\end{enumerate}

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{figures/twoterm.pdf}
\hspace{0.2in}
\includegraphics[scale=0.85]{figures/colorcode.pdf}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $J_0=0$, and $J=2$, following
the example shown in \citet{Ambikasaran:2015}.}
\figurelabel{matrix_structure}
\end{figure}

>>>>

Another special case of the \celerite\ model of great physical interest is a
stochastically-driven simple harmonic oscillator.
The differential equation for this system is
\begin{equation}
    \left[\frac{\dd^2}{\dd t^2} + \frac{\omega_0}{Q}\,\frac{\dd}{\dd t}
    + \omega_0^2\right]\, y(t) = \epsilon(t)
\end{equation}
where $\omega_0$ is the frequency of the undamped oscillator, $Q$ is the
quality factor of the oscillator, and $\epsilon(t)$ is a stochastic driving
force.
In the limit of an infinite time series and white random forcing, the PSD of
this equation is given by \citep{Anderson:1990}
\begin{equation}\eqlabel{sho-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0\,\omega_0^4}
    {(\omega^2-\omega_0^2)^2 + \omega_0^2\omega^2/Q^2}
\end{equation}
where $S_0$ is proportional to the power at $\omega = \omega_0$, $S(\omega_0)
= \sqrt{2/\pi}\,S_0\,Q^2$.
The power spectrum in \eq{sho-psd} matches \eq{celerite-psd} if
\begin{eqnarray}\eqlabel{sho-complex}
a_j &=& S_0\,\omega_0\,Q \\
b_j &=& \frac{S_0\,\omega_0\,Q}{\sqrt{4\,Q^2-1}} \\
c_j &=& \frac{\omega_0}{2\,Q}\\
d_j &=& \frac{\omega_0}{2\,Q} \sqrt{4\,Q^2-1} \quad,
\end{eqnarray}
for $Q \ge \frac{1}{2}$.
For $0 < Q \le \frac{1}{2}$, \eq{sho-psd} can be captured by a pair of \celerite\
terms with parameters
\begin{eqnarray}\eqlabel{sho-real}
a_{j\pm} &=& \frac{1}{2}\,S_0\,\omega_0\,Q\,\left[ 1 \pm
        \frac{1}{\sqrt{1-4\,Q^2}}\right] \\
b_{j\pm} &=& 0 \nonumber\\
    c_{j\pm} &=& \frac{\omega_0}{2\,Q}\,\left[1 \mp \sqrt{1-4\,Q^2}\right]
    \nonumber\\
d_{j\pm} &=& 0 \quad. \nonumber
\end{eqnarray}

@@

@@
